\begin{minipage}{\textwidth} \centering Analyzing rasters, vectors and time series using new Python interfaces in GRASS GIS 7 \bigskip \end{minipage}

### 2015-03-30 grassposter/2015_EGU_G7_Python/main.tex
two paragraphs about modules, addons and scripts
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64946 15284696-431f-4ddb-bdfa-cd5b030d7da7

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{GRASS GIS modules, addons and Python scripts}}{
The GRASS GIS Addons ensure long-term preservation of the code.
Well maintained modules in Addons can be moved to GRASS GIS core.
and running code from IDE
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{GRASS GIS modules, addons and Python scripts}}{
A Python script can by turned into a GRASS GIS modules by adding a definition of the interface.
Also, GRASS GIS modules expect to be executed in GRASS GIS session.
Python scripts which are using GRASS GIS can be written in a way that GRASS GIS session is not required;
the setup of a necessary environment is done in the script itself.
% running code from IDE

The GRASS GIS Addon repository ensures vendor-independent long-term preservation of the code
and ensures an easy distribution of module to individual users.
Well maintained modules in Addons can be moved to GRASS GIS core.
}
